Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-22 paper/snakemajoranas.tex
remove length details, and wf -> Majorana wf
improve fig caption

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/phasediagrams}
\caption{Part the wave function of a straight system (a) and a zigzag system (b) of length $L=\SI{3900}{\nm}$ but only the first period ($\SI{1300}{\nm}$) is plotted.
The phase diagrams (c) and (d) display $E_\textrm{gap}(B_x, \mu)$ at $\phi=\pi$ and (e) and (f) display $E_\textrm{gap}(B_x, \phi)$ at $\mu=\SI{10}{\meV}$, where $E_\textrm{gap}$ is the smallest gap in the dispersion relation.
Subplots (c) and (e) correspond to system (a), and (d) and (f) correspond to system (b).
The brown dot in the phase diagrams indicate the largest gap in the parameter space for the straight system and the parameter values for which the wavefunctions (a) and (b) are plotted.
Additionally, in subplot (c) we plot the phase boundaries because they are too narrow to see.
In (a) and (b) we note the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$, and see that both of these are more than an order of magnitude better for the zigzag system, even though these are plotted for the most optimal parameters for the straight system at $\mu=\SI{10}{\meV}$.
The remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
\label{fig:phasediagrams}}
\end{figure}

@@

\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing Majorana length.}
The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length, which enables experimentalists to create significantly shorter devices.
Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner and more stable topological region.

>>>>

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/phasediagrams}
\caption{A comparison of a straight device (left panels) and a zigzag one (right panels).
The top panels show the Majorana wave functions, near the left edge of the system, at the value of $B_x$ for which $E_\textrm{gap}$ is maximized in a straight geometry for $\mu=\SI{10}{\meV}$ and $\phi=\pi$ as well as the values of the gap and the Majorana size.
The other panels show gap as a function of $\mu$ and $B_x$ at $\phi=\pi$ (middle panels) and as a function of $\phi$ and $B_x$ at $\mu=\SI{10}{\meV}$ (bottom panels).
The dashed lines and the dot indicate the parameters used in the other panels.
Additionally, in subplot (c) we overlay the phase boundaries.
The remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
\label{fig:phasediagrams}}
\end{figure}

@@

\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing Majorana length.}
The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length, which enables experimentalists to create significantly shorter devices.
% The Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are more than an order of magnitude better for the zigzag system, even though these are plotted for the optimal parameters for the straight system at $\mu=\SI{10}{\meV}$.  % From phase diagram figure
Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner and more stable topological region.
